---
title: "L00 Setup"
subtitle: "Data Science 1 with R (STAT 301-1)"
author: "Hannah Li"
format:
  html:
    toc: true
    embed-resources: true
    link-external-newwindow: true
execute:
  warning: false
from: markdown+emoji 
editor_options: 
  chunk_output_type: console
---

::: {.callout-tip icon="false"}
## Github Repo Link

<https://github.com/hannahs-li/diwl>
::: 

## Tasks

Complete the following tasks. For each task you'll need to simply **indicate that you have completed the task**.

### Task 1 ✅ 

Download and install [R Software](https://cran.rstudio.com/).

### Task 2  ✅ 

1.  Download and install [RStudio](https://www.rstudio.com/products/rstudio/download4/).
2.  Open RStudio and ensure it and R have been properly installed.
3.  Go to **Tools** \> **Global Options** and change the two indicated settings below and click **Apply**. Your other options are likely different than what is pictured. This is okay and we suggest you leave them as is until you become more familiar with RStudio.

### Task 3 ✅ 

```{r}
library(tidyverse)
library(skimr)
library(janitor)
library(nycflights13)
library(gapminder)
library(Lahman)
library(devtools)
library(tutorial.helpers)
library(r4ds.tutorials)
```

Install the following packages:

-   `tidyverse`
-   `skimr`
-   `janitor`
-   `nycflights13`
-   `gapminder`
-   `Lahman`
-   `devtools`
-   `tutorial.helpers`
-   `r4ds.tutorials`

### Task 4 

Create a [GitHub](http://www.github.com/) account.

Install git and connect to RStudio. See textbook [Happy Git and GitHub for the useR](https://happygitwithr.com/) Chapters 1 - 9.

### Task 5 ✅ 

Since organization is essential for any data science project or work, we should begin by setting up an organizational structure for this course and its contents.

0.  Setup a directory/folder on your laptop that will contain all your materials and work for this course. You may already have one setup and named. We will setup this directory and call it `stat301-1`. Where this is located on your laptop is completely up to you.

1.  Within `stat301-1/`, place a copy of the course syllabus for future reference. We also will create a new sub-directory that will contain all labs for this course. For ease let us call it `labs`. So now we have `stat301-1/labs/`.

2.  Open RStudio and create a "New Project" using "Version Control" -\> "Git"

3.  Copy the URL from GitHub. Browse so that you place this project within the `stat301-1/labs/` folder that you created.

4.  Rename `template_L00.qmd` to your `Lastname_Firstname_L00.qmd`

5.  Render the file with `Cmd/Ctrl + Shift + K` or click the **Render button**.

### Task 6 (optional)  ✅ 

It is always handy to have a versatile text editor and I would suggest downloading [Sublime Text](https://www.sublimetext.com/). It is free to use.

## Exercises

### Exercise 1 ✅ 

Suppose a random variable $X$ has finite variance, then as we take larger random samples (i.e. as $n$ increases) we have that $$\bar{X} \sim N\left(\mu_{\bar{X}}=\mu_X, \sigma^2_{\bar{X}} = \frac{\sigma_X^2}{n}\right)$$ This is an informal statement of which important statistical theorem?

::: {.callout-tip icon="false"}
## Solution

Central Limit Theorem
:::

### Exercise 2 ✅ 

Create a code chunk and assign the value 5 to `x` and the value 3 to `y`. Then print `x * y`.

::: {.callout-tip icon="false"}
## Solution

```{r}
#| label: ex2

x <- 5
y <- 3

print(x*y)
```
:::

## Reminders

::: {.callout-tip icon="false"}
-   Render often!

-   Make sure you commit and push all changes to GitHub! Do this EVERY TIME you are done working. NOT just before you are ready to submit to Canvas. You will often have MANY commits... think of each commit as a save spot.

-   Upload your .html to Canvas.
:::

------------------------------------------------------------------------
